---
title: "week01_exercise part B"
format: html
editor: source
---

## install and load the needed libraries

First, I need to install and load all the libraries I'll need for this exercise.

```{r}
#install.packages("tidyverse")
library(tidyverse)
```

## R code that samples 100 values from a log-normal distribution

Then, I need to create some data to do the exercise with.
Mean = 166.69
Standard deviation = 79.03

```{r}
?rlnorm
x <- rlnorm(100, meanlog = 5, sdlog = 0.5)
x

mean(x)
sd(x)
```

## using the ggplot2 package, create a histogram of the sampled data on both the linear and log scales 

Using the created vector containing log-normal distributed values, I plot a histogram on both the linear and log scales. 

```{r}
?hist
hist(x)
hist(log(x))
```

## create also a violin plot

Further, I need to do a violin plot, which does not accept data in form of a vector. Thus, I create a data frame with some random information. I changed the variable "Student" from a number into a factor and rearranged the data frame from wide to long format to be able to plot a violin plot.
Mean (Grades) = 4.97
Standard deviation (Grades) = 0.75

```{r}
df <- data.frame(Student = c(1, 2, 3, 4, 5), 
                 Grade1 = c(4, 6, 5.5, 4.5, 5.75), 
                 Grade2 = c(3.5, 6, 5.25, 4, 4.5),
                 Grade3 = c(5, 5.5, 5, 5, 5))
df
str(df)
df$Student <- as.factor(df$Student)

df <- df %>%
  pivot_longer(cols = c(Grade1, Grade2, Grade3),
               names_to = "Year",
               values_to = "Grades")

?geom_violin
ggplot(df, aes(x = Student, y = Grades)) + geom_violin()

mean(df$Grades)
sd(df$Grades)
```
